---
title: "Naming Conventions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Naming Conventions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}

```

# Naming Conventions in R

> *Note*
> 

## File Naming Conventions

### R Files

Files containing R code (i.e. `*.R`) should be named using the following guidelines:

- Use lowercase letters and underscores, also known as `snake_case`.

- Use a descriptive name that clearly indicates the purpose of the file.

- Use a *"noun_verb"* syntax to clearly indicate the purpose of the primary object
  the code within the file interacts with. This will help in grouping related functions
  and code while also making it easier to navigate the codebase.

#### Example: Git Functions and Files

For example, in this package, we provide a variety of functions for working with 
`git`. These functions are stored inside R files under the `R/` folder using the
naming syntax `git_*.R`. For example, `git_config.R`, `git_ignore.R`, `git_attributes.R`,
and so on.

The complete set of git R files and their corresponding exported functions are
as follows:

- `git_config.R`:
  - `git_config_get()`
  - `git_config_set()`
  - `git_config_unset()`
  - `git_config_list()`
  - `git_config_assert()`
  - `git_config_path()`
  - `git_config_edit()`

- `git_ignore.R`:
  - `git_ignore()` (alias for `git_ignore_add()`)
  - `git_ignore_add()`
  - `git_ignore_remove()`
  - `git_ignore_list()`
  - `git_ignore_assert()`
  - `git_ignore_path()`
  - `git_ignore_edit()`
  
- `git_attributes.R`:
  - `git_attributes()` (alias for `git_attributes_add()`)
  - `git_attributes_add()`
  - `git_attributes_remove()`
  - `git_attributes_list()`
  - `git_attributes_assert()`
  - `git_attributes_path()`
  - `git_attributes_edit()`

- `git_hooks.R`:
  - `git_hooks()` (alias for `git_hooks_add()`)
  - `git_hooks_add()`
  - `git_hooks_remove()`
  - `git_hooks_list()`
  - `git_hooks_assert()`
  - `git_hooks_path()`
  - `git_hooks_edit()`
  
- `git_init.R`:
  - `git_init()`

You can see that the naming convention `git_*.R` helps in grouping related functions
together and makes it easier to navigate the codebase.

### Vignettes and RMarkdown

Vignettes and RMarkdown files should be named using the following guidelines:

### Data Files

Data files should be named using the following guidelines:

### Tests

Test files should be named using the following guidelines:

### Documentation

Documentation files should be named using the following guidelines:

#### Roxygen Documentation

Roxygen function documentation should be named using the following guidelines:

## Function Naming Conventions

### Function Names

Function names should be named using the following guidelines:

### Argument Names

Function argument names should be named using the following guidelines:

### Return Values

Function return values should be named using the following guidelines:

## Variable Naming Conventions

### Variable Names

Variable names should be named using the following guidelines:

### Constants

Constants should be named using the following guidelines:

## Package Naming Conventions

### Package Names

Package names should be named using the following guidelines:

### Namespace

Namespace files should be named using the following guidelines:

## Project Naming Conventions
