---
title: "shiny"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{shiny}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
# library(noclocksr)
```

## Shiny Concepts

## Shiny Cards

Card Types:

- User Profile Card (`user_card()`): A card that displays user information.
- Metric Cards: Cards for displaying metrics:
  - Value Box (`val_box()`): A card that displays a single value.
  - Summary Box (`summary_box()`): A card that displays a summary of a metric.
  - Info Box (`info_box()`): A card that displays information.
- Basic Cards: Basic cards for displaying information:
  - Info Card (`info_card()`): A card that displays information.
  - Alert Card (`alert_card()`): A card that displays an alert.
  - Warning Card (`warning_card()`): A card that displays a warning.
  - Error Card (`error_card()`): A card that displays an error.

- Flip Card (`flip_card()`): A card that flips between two sides.

